Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
HRIR results

\Cref{fig:interpolation} shows the filter $h$, the kernel $k_{f\cond h}$, and a sample $f\cond h \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ while the filter is interpolated from one that satisfies $h(0)=0$ to one that satisfies $|h(0)|>0$. Note that the sample appears smooth for $h(0)=0$ and becomes rougher as $|h(0)|$ increases.

@@

\subsection{Head-Related Transfer Function}
The head-related transfer function (HRTF) describes how the reception of sound by the ear depends on the position from which the sound originates.

>>>>

\Cref{fig:interpolation} shows the filter $h$, the kernel $k_{f\cond h}$, and a sample $f\cond h \sim \mathcal{GP}(0,k_{f\cond h}(t-t'))$ while the filter is interpolated from one that satisfies $h(0)=0$ to one that satisfies $|h(0)|>0$. Note that the sample appears smooth for $h(0)=0$ and becomes rougher as $|h(0)|$ increases. {\color{red} something about pointyness?}

@@

\subsection{Head-Related Impulse Response}
The head-related impulse response (HRIR) describes how the reception of sound by the ear depends on the position from which the sound originates.
\begin{figure*}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
        $k_{f\cond h}$ & $h$ & $k_{f\cond h}$ & $h$
    \end{tabularx}
    \includegraphics[width=.49\linewidth, height=3cm]{resources/hrtf_gpcm.pdf}
    \includegraphics[width=.49\linewidth, height=3cm]{resources/hrtf_cgpcm.pdf}
    \caption{HRIR. Here {\color{red}red} denotes truth, {\color{blue}blue} denotes quantities learned through the MF approximation, and {\color{mycyan}cyan} denotes quantities learned through the SMF approximation. All signals are normalised to unity power.}
    \label{fig:hrir}
\end{figure*}
